Modelling the Lymphatic Metastatic Progression Pathways of OPSCC from Multi-Institutional Datasets

### 2023-01-03 src/tex/ms.tex
[showyourwork] overleaf sync

% Define document class
\documentclass[twocolumn]{aastex631}
\usepackage{showyourwork}
\usepackage{multirow}
\usepackage{nicefrac}

@@

@@

@@

\begin{table*}
    \centering
    \variable{output/results_table.tex}
    \caption{Model comparison results from the base graph and the extended graph we chose as the ``winnning'' model. For both \glspl{dag} we show the log-evidence, computed via thermodynamic integration, the negative one half of the \gls{bic}, as well as the maximum log-likelihood that was encountered during the final \gls{mcmc} sampling round.}
    \label{table:evidence}
\end{table*}

>>>>

% Define document class
\documentclass[twocolumn]{aastex631}
\usepackage{showyourwork}
\usepackage{multirow}
\usepackage{nicefrac}
\usepackage{wasysym}

@@

\begin{table*}
    \centering
    \input{output/data_table.tex}
    \caption{Prevalence of involvement patterns in the multi-centric dataset. An involvement pattern is characterized by the state of the six \glspl{lnl}: A red dot means the \gls{lnl} was reported to be metastatic, a green dot means it was determined to be healthy and a question mark means that the prevalence was marginalized over the state of this \gls{lnl}.}
    \label{table:data_prevalence}
\end{table*}

@@

\begin{figure}
    \script{thermo_int.py}
    \centering
    \includegraphics[width=\linewidth]{figures/thermo_int.png}
    \caption{Placeholder}
    \label{fig:thermo_int}
\end{figure}

@@

\begin{table*}
    \centering
    \input{output/results_table.tex}
    \caption{Model comparison results from the base graph and the extended graph we chose as the ``winnning'' model. For both \glspl{dag} we show the log-evidence, computed via thermodynamic integration, the negative one half of the \gls{bic}, as well as the maximum log-likelihood that was encountered during the final \gls{mcmc} sampling round.}
    \label{table:evidence}
\end{table*}
